LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-11-28 main.tex
Revise grammar in ocean data section

\Cref{f:ocean dataset LCS} shows the positions of elliptic and hyperbolic LCSs on 22 November 2006, which is the same time instant analysed in \citet{haller13:_coher_lagran,haller14:_adden_coher_lagran,beron-vera13:_objec_agulh}. Here the integration time is chosen as $T = 30$ days, as opposed to 90 days in the cited references, to avoid tangling of hyperbolic LCSs. Our analysis via LCS Tool reveals five coherent eddy boundaries. The large coherent eddy at $(3,-32)$ has a non-stretching boundary, i.e., $\lambda = 1$. It corresponds to eddy \#2 in Figure~3 of \citet{beron-vera13:_objec_agulh}. Additionally, four smaller coherent eddy cores are found. They do not stay coherent over a time of 90 days. All closed orbits are stable under increased spatial resolution for the Cauchy-Green strain tensor field. Repelling LCSs (red) and attracting LCSs (blue) are superimposed over the plot of FTLE values. The hyperbolic LCSs determine the deformation of the fluid in-between coherent eddy cores.

>>>>

\Cref{f:ocean dataset LCS} shows elliptic and hyperbolic LCSs on 22 November 2006, the same time as analysed in \citet{haller13:_coher_lagran,haller14:_adden_coher_lagran,beron-vera13:_objec_agulh}.
In those references, the integration time is 90 days.
We use a shorter time to avoid tangling hyperbolic LCSs.
Our analysis via LCS Tool reveals five coherent eddies.
The largest, at $(3,-32)$, has a non-stretching boundary, i.e., $\lambda = 1$.
It corresponds to eddy \#2 in figure~3 of \citet{beron-vera13:_objec_agulh}.
Four additional smaller coherent eddies are found.
They do not stay coherent over 90 days.
The hyperbolic LCSs determine the deformation of the fluid between coherent eddies.
